Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-10-11 main.tex
merged

    \begin{figure}[tb]
        \centering
        \includegraphics[width=1.1\columnwidth] {images/makespan_relations_by_wf_size}
        \caption{Relative makespans produced by the heuristics to the makespan produced by the baseline, by workflow
        size. Smaller is better. \skug{CHECK this pictue. It might have a wrong mean function}}
        \label{fig:ms-relations-by-workflow}
        \vspace{-0.3cm}
    \end{figure}

@@

@@

    \begin{figure}[tb]
        \centering
        \includegraphics[width=1.1\columnwidth] {images/runtimes-absolute}
        \caption{Running times of the heuristics and the baseline.}
        \label{fig:runtimes-abs}
        \vspace{-0.3cm}
    \end{figure}

>>>>

    \begin{figure}[tb]
        \centering
        \includegraphics[width=1.1\columnwidth] {images/makespan_relations_by_wf_size}
        \caption{Relative makespans produced by the heuristics to the makespan produced by the baseline, by workflow
        size. Smaller is better.}
        \label{fig:ms-relations-by-workflow}
        \vspace{-0.3cm}
    \end{figure}

@@

    Relative makespans to the baseline (including the invalid values of the baseline) are shown in Fig.~\ref{fig:ms-relations-by-workflow-constrained}.

    \begin{figure}[tb]
        \centering
        \includegraphics[width=1.1\columnwidth] {images/makespan_relations_by_wf_size-constrained}
        \caption{Relative makespans produced by the heuristics to the makespan produced by the baseline, by workflow
        size. Smaller is better.}
        \label{fig:ms-relations-by-workflow-constrained}
        \vspace{-0.3cm}
    \end{figure}

@@

    %\begin{figure}[tb]
    %    \centering
    %    \includegraphics[width=1.1\columnwidth] {images/runtimes-absolute}
    %    \caption{Running times of the heuristics and the baseline.}
    %    \label{fig:runtimes-abs}
    %    \vspace{-0.3cm}
    %\end{figure}
